

\section{Transaction Abstraction }

An abstract transaction is a generalized representation of a blockchain transaction that abstracts away the specific details of any particular blockchain protocol. It provides a standardized format for encapsulating all necessary information required for transaction execution, such as sender/receiver addresses, transaction data, gas limits, proofs, and other metadata. This abstraction ensures that transactions can be processed seamlessly across different blockchain networks, regardless of their underlying protocols, consensus mechanisms, or data structures. In simpler terms, an abstract transaction is a unified language that bridges the differences between blockchains, enabling communication and interaction across multiple networks.


An abstract transaction in the Omnichain ecosystem is designed to carry all the necessary information for cross-chain execution. The following is a detailed format:
\begin{itemize}
    \item \textbf{Header:}
    The header contains metadata about the transaction:
    \begin{itemize}
        \item \textsf{Transaction ID}: Unique identifier for the transaction.
        \item \textsf{Source Chain ID}: Identifier of the chain from which the transaction originates.
        \item \textsf{Target Chain ID(s)}: Identifier(s) of the destination chain(s).
        \item \textsf{Nonce}: A unique number to ensure transaction uniqueness and prevent replay attacks.
        \item \textsf{Timestamp}: Time of transaction creation for ordering and validation.
    \end{itemize}
    \item \textbf{Payload:}
    The payload includes the core logic and data of the transaction:
    \begin{itemize}
        \item \textsf{Sender Address}: Address of the user or entity initiating the transaction.
        \item \textsf{Receiver Address}: Target address on the destination chain.
        \item \textsf{Action Type}: Specifies the transaction type (e.g., transfer, invocation of smart contracts).
        \item \textsf{Data/Call Parameters}: Encoded data required to execute the action on the target chain (e.g., function arguments for contract calls).
        \item \textsf{Asset Details (if applicable)}:\\
            Asset ID: Token or asset being transferred.\\
            Amount: Quantity of the asset being transferred.
    \end{itemize}

    \item \textbf{Execution Details:}
    Information about the execution context:
    \begin{itemize}
        \item \textsf{Gas Limit}: Upper limit for gas usage (abstracted from the user, automatically handled by the system).
        \item \textsf{Fee Payment Details}: Specifies how fees are handled, such as being paid in native tokens or abstracted through relayers.
        \item \textsf{Batch Information}: Indicates if the transaction is part of a batch (used for solver optimization).
    \end{itemize}

    \item \textbf{Proofs and Signatures:}
    Cryptographic elements to ensure validity and security:
    \begin{itemize}
        \item \textsf{Source Chain Proof}: Proof confirming execution on the source chain.
        \item \textsf{Cross-Chain Proof}: Generated by the Prover Network for the state transition function.
        \item \textsf{Signatures}: Cryptographic signatures from the sender or relayer for authorization.
    \end{itemize}

    \item \textbf{Settlement Instructions:}
    Instructions for final settlement:
    \begin{itemize}
        \item \textsf{Target Contract Address}: Smart contract on the destination chain to execute the transaction.
        \item \textsf{Confirmation Requirement}: Specifies whether the execution of the source chain must be confirmed before settlement.
        \item \textsf{Rollback Mechanism}: Conditions and actions to handle failed transactions.
    \end{itemize}
\end{itemize}

 

    

